A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-18 paper.tex
figure 1

The application which is the study of this paper is called \emph{TauRoast}
It searches for cases where the the Higgs boson decays to two tau leptons.
The leptons are not observed directly, but by the particle showers
that they generate.  So, the analysis must search for detector
events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
the events of interest (Higgs decays) from all other events and
are also used in further statistical analysis.

@@

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment was under continuous change.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the experiment deprecated the use of CVS for obtaining
the software.  While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

@@

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physicists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

@@

The relationship of different roles involved in the experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
Then the package, together with
its map file and description file will be published. When
another researcher wants to repeat the experiment, one copy of the package will be downloaded into the new machine and the application can be repeated.

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

@@

With the help of one
virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

@@

\section{Evaluation}
We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

@@

Table~\ref{table:time-2nd3rd} also illustrates the time used to
obtain the filename list and generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the experiment
separately.

@@

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the experiment on each machine.
All the machines adopt x86\_64 hardware platform and Linux OS.
Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.

>>>>

The application which is the study of this paper is called \emph{TauRoast}
It searches for cases where the Higgs boson decays to two tau leptons.
The leptons are not observed directly, but by the particle showers
that they generate.  So, the analysis must search for detector
events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
the events of interest (Higgs decays) from all other events and
are also used in further statistical analysis.

@@

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment was under continuous change.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the application deprecated the use of CVS for obtaining
the software.  While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

@@

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this application, the machine used for the application is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physicists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

@@

The relationship of different roles involved in the application preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
Then the package, together with
its map file and description file will be published. When
another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

@@

With the help of one
virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the application.

@@

\section{Evaluation}
We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the application was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

@@

Table~\ref{table:time-2nd3rd} also illustrates the time used to
obtain the filename list and generate the package. 
The time used for these two steps is longer than the execution time,
because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
However, 
this is only done once.
Once the package is
generated, many users can directly obtain the package and repeat the application 
separately.

@@

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the application on each machine.
All the machines adopt x86\_64 hardware platform and Linux OS.
Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.
